\chapter{Introduction} % Main chapter title

\label{Chapter 1} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Introduction } % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

\section{Introduction}
Unscheduled downtime in CNC machines due to tool wear, spindle failures, and thermal issues leads to significant economic losses in manufacturing. Traditional maintenance is reactive or periodic, inefficient for Industry 4.0 demands. This project develops an AI-driven Predictive Maintenance (PdM) system integrating real-time IoT sensor data with ML models for fault forecasting and CAD/CAM workflow optimization using STEP-NC standards \cite{luo2020hybrid,srivastava2023stepnc}.

The system monitors vibration, temperature, acoustics from CNC setups, computes features on edge (ESP32), and uses cloud ML (RF for classification, LSTM for RUL) with React dashboard for visualization, labeling, retraining.

\section{Problem Statement}
G-code limitations hinder seamless CAD/CAM-CNC integration; heterogeneous CAD APIs and lack of PdM cause 20-50\% downtime. Need lightweight IoT+ML PdM addressing data scarcity, interpretability, real-time constraints \cite{cinar2020mlpdm,wakhare2023optimizing}.

\section{Motivation}
Industry 4.0 requires intelligent manufacturing: PdM reduces costs by 30\%, STEP-NC enables cloud CAM. Aligns with literature calls for hybrid ML+Digital Twin systems \cite{paolanti2018mlindustry4}.

\section{Contributions}
- IoT edge-cloud PdM pipeline for CNC (multi-sensor → RF/LSTM).
- CAD/CAM integration blueprint via STEP-NC API.
- Real-time dashboard (cnc\_automation\_project frontend/backend) with retraining.
- Literature synthesis filling gaps in lightweight, XAI-enabled PdM \cite{sarikaya2024predictive,zhang2025camaservice}.

