% Chapter Template

\chapter{Features} % Main chapter title

\label{Chapter 2}


\lhead{Features} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

The Device was intended to be multi-tasking. The device has two different modes, namely ``Data-Collection Mode'', ``Data-Prediction Mode'', for serving two unique functionalities.

\section{Data-Collection Mode}
Our Device will collect the data from the sensors and compute the statistical features like mean, max, min and variance for each of the 6 sensor parameters [ ax,ay,az,gx,gy,gz] and send to the backend server to store for future labelling purposes.

\section{Data-Prediction Mode}
Device will collect and compute the statistical features of sensor data and send the server and server will use the saved ML model to do the prediction and will post a alert message in a MQTT  Topic if there is a fall , our device wil give a alert if any message posted in that MQTT topic.

\section{Real-time Frontend Dashboard and Retraining Feature}
This System also provides us a real-time frontend dashboards and also retraining feature of the ML model in the form of button.

\subsection{Analytics Page}
It Provides a real-time dashboard which visualises the last 10 min status of the person in which we can observe the whether there is a fall action noted or not.

\subsection{Training Page}
All the unlabelled data points from the database are fetched into single table and a labelling option will be made available once a datapoint is labelled it will be automatically updated in the database and in the frontend as well without need of refreshing the page.

\subsection{Model Retraining}
This Button Enables us to re-train the model, on the new dataset which contains all the labeled data.